\documentclass{resume} 
\usepackage{graphicx}
\usepackage{comment}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sina Maria Schlegel} 

\address{Email: sinamaria.schlegel@student.unisg.ch; Mobile: +41 79 530 16 80}

\begin{document}

\begin{rSection}{Education}

\textbf{Bachelor of Arts (B.A. HSG) in Economics} \hfill Sep. 2023 - Aug. 2026\\
University of St.Gallen (HSG)
\hfill \textit{St.Gallen, Switzerland}
\begin{itemize}
    \setlength\itemsep{-0.5em}
    \item \textbf{Current GPA:} 5.63 / 6.00
    \item \textbf{Incoming Exchange:} Università Bocconi, Milan, Italy\\
    \quad \textit{Coursework:} Mathematical Modelling for Finance; Stochastic Processes and Simulations in Natural Sciences; Advanced Python Programming for Finance.
    \item \textbf{Academic focus:} Data Science and Statistical Modelling; Econometrics and Empirical Methods; Time-Series Analysis; Data Handling; Advanced Microeconomics; Game Theory.
    \item \textbf{Honors:} "Monique Dornonville de la Cour-Stiftung" Excellence Scholarship awarded by the University of St.Gallen in recognition of excellent academic achievement.
    \item Completed Certificate in Data Science worth 24 ECTS (GPA: 5.79 / 6.00).
    \item \textbf{Bachelor's Thesis} (ongoing): Probabilistic Forecasting for Swiss Inflation – Comparing Machine Learning and Econometric Models using Quantile Regression Forests and Bayesian VARs.
\end{itemize}

\textbf{Language Stay} \hfill Oct. 2022 - Dec. 2022\\
	St.Giles International English Language School\hfill \textit{Brighton, United Kingdom}

	\textbf{Bachelor’s Program in Mathematics } \hfill Sep. 2021 - Oct. 2022\\
	Swiss Federal Institute of Technology (ETH) Zurich\hfill \textit{Zurich, Switzerland}
	\begin{itemize}
    	\setlength\itemsep{-0.5em}
    	\item \textbf{Academic focus:}  Computer Science (C++), Fundamentals of Analysis, Physics, and Linear Algebra.
            \item Gained foundational knowledge in rigorous proof-based mathematics and computational thinking.
	\end{itemize}
    \textbf{Swiss Matura (Swiss A-Levels)} \hfill Aug. 2017 - Aug. 2021\\
	Kantonsschule Sargans\hfill \textit{Sargans, Switzerland}
	\begin{itemize}
    	\setlength\itemsep{-0.5em}
    	\item \textbf{GPA:} 5.27/6.00
            \item \textbf{Concentration:} Biology and Chemistry
            \item \textbf{Supplementary Subject:} Economics and Law
            \item \textbf{Elective Courses:} Spanish; 3D Printing; Financial Accounting
    	\item \textbf{Extracurricular Activities:} Part-time job as an English tutor for a middle school student (Aug. 2019 - Jun. 2021) 
	\end{itemize}
	\end{rSection}

    
    \begin{rSection}{Professional Experience}


	\textbf{Research Assistant at the Chair of Mathematics (10\%) } \hfill Sep. 2024 - present\\
	University of St.Gallen (HSG)  \hfill \textit{St.Gallen, Switzerland}
	\begin{itemize}
        \setlength\itemsep{-0.5em}
        \item Produce videos to introduce students to mathematical foundations, communicating complex concepts in accessible terms.
    	\item Co-develop supplementary course materials, including problem sets and solutions, for first-year mathematics courses
    	\item Provide direct research support for faculty projects; responsibilities include conducting comprehensive literature reviews, performing preliminary data analysis in R, and generating statistical figures using \LaTeX.
	\end{itemize}
    


	\textbf{Trainee in Intermediary Banking } \hfill Jan. 2023 - Sep. 2023\\
	VP Bank (Liechtenstein) AG\hfill \textit{Vaduz, Liechtenstein}
	\begin{itemize}
        \setlength\itemsep{-0.5em}
            \item  Ensured MiFID II and KYC compliance for a portfolio of international intermediary clients, reducing onboarding defi
            ciencies by identifying and resolving documentation issues prior to submission.
            \item Managed the end-to-end onboarding workflow for new client accounts, liaising between Intermediaries, Team Leads, and
            Client Advisors to ensure seamless data integration into CRM systems.
            \item Handled general administrative tasks and supporting Intermediaries Manager, Team Leads, and Client Advisors in daily operations.
            \item Improved team workflow by creating a centralized Excel dashboard to track pending tasks and deadlines for client
 accounts, enhancing coordination between advisors and support staff
	\end{itemize}

	\end{rSection} 
    
	\begin{rSection}{SKILLS}

	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
	Technology &  Office; Python; C++; CAD; R; Git; SQL; \LaTeX \\


	Languages & German (Native); English (C1); French (B2); Spanish (B1) \\
	\end{tabular}\\
	\end{rSection}




\end{document}
